% An example latex source file for your reports
%
% Do NOT alter from here to "\begin{document}"
%
% I extract the text of your report between \begin{document} and \end{document},
% and ignore any changes that you make to this "preamble" (this initial
% part of the tex file, before \begin{document} ).  Please do not use any
% additional packages or create your own latex commands.

\documentclass[11pt,usenames,dvipsnames]{article}
\usepackage[left=3cm,top=1cm,right=3cm,bottom=1cm,marginparwidth=2cm]{geometry}
\usepackage{siunitx}
\usepackage{gensymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\PassOptionsToPackage{hyphens}{url}\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{mathtools} % required for $\coloneqq$
\pagestyle{empty}

\begin{document}

% CHANGE THE FOLLOWING INFORMATION:

\begin{center}
  \large\textbf{PHYS 342, Spring 2020: Report 3} \\ \vspace{10 pt}
  \textbf{Robie Hennigar (with contributions from Ali Ramadhan and Jim Martin)} \\
  \normalsize ID: 13333337 \\
\end{center}

% FOR YOUR REPORT DELETE EVERYTHING THAT FOLLOWS,
% UP UNTIL (BUT NOT INCLUDING) THE:
%   \end{document}
% LINE

I came away from this assignment with much more confidence in my understanding of Ampere's law and improved my ability to deduce the ``shape" of a magnetic field produced by a given current distribution.  However, as I tackled some of the later problems, I realized that my multivariate calculus is weaker than I had anticipated.  I realize this a crucial component of the course, so I have made plans with a classmate to review the relevant sections in the first chapter of Griffiths this weekend. I think it might benefit future students if the assignment had some warm-up questions from the first chapter to remind us of the most important concepts from multivariate calculus. Below I will go into more detail about the specifics of the assignment.

I was able to complete problems (1) through (3) without referring to the solutions for help. In these problems I benefited from having a good working understanding of Ampere's law. I found problem (3) part (c) particularly interesting, since the result is the speed of light, which I had not anticipated.  I was wondering, \textbf{ is there any reason why I should expect such a result on physical grounds?}

I struggled with part (d) of problem (4) because it was unclear to me how to obtain a current density here.  I was able to produce the correct answer after referring to the solutions, but I did not understand, for example, the equality made in the second line on page (3) of this solution: that $I/v = \lambda$.  A friend told me that it follows from dimensional analysis, which I now understand, but I was wondering: \textbf{ is there is any way to understand this result without resorting to dimensional analysis?}

I made a silly mistake when first attempting problem (5) -- I forgot to use $\nabla$ in cylindrical coordinates. Otherwise it was an easy solve. I understand that the forms for the derivative operator in different coordinates will be provided on the midterm and final exam, otherwise I would definitely be putting this form for $\nabla$ on my cheat sheet!

Problem (6) provided useful experience with vector calculus identities.  However, it also made me realize that I am just not comfortable with these yet, especially when they involve the derivative operator.  After investing some time---and making a few mistakes---I was able to obtain the correct answer.  I did not understand the second part of the problem about the uniqueness of the vector potential, though.  I can understand the solutions, but I have to admit I would have never thought to add the particular choice of function to $\vec{A}$ that is done in the last few lines of the solution. Maybe the solutions can provide some motivation for this step?

I completed problem (7) without difficulty.  In fact, it made me feel clever since I realized that the result from the previous question could be applied here.

I had a good deal of trouble with problem (8) and had to follow the solutions directly in order to make progress.  Even then there were aspects I did not understand---for example, why we could set terms such as $\vec{A}(0,y,z)=0$ (see eq. (12) in the solution to this question).  I am unsure if I truly understand this problem, or was just able to follow the solutions.  I am going to wait a few days and then tackle this problem again to see if I can now complete it without referring to the solutions along the way. I feel like the solutions could be made clearer using the TA's explanation.

I did not have time to complete part (c) of problem 8 nor any of problem (9).  I will be working on these over the weekend.

For the next assignment, I am going to work on one problem a day (using a fixed amount of time), to improve my long-term retention of the material, rather than waiting until closer to the deadline.

I am still unsure if the magnetic vector potential has a physical interpretation or if it's just a useful mathematical construction. I would appreciate it if this issue was covered in the notes more clearly or if there was a related assignment question.

\newpage

\noindent
{\bf Some additional examples of useful latex stuff:}\\

\noindent
Example of the use of enumerated lists:  Summarizing the problems that I worked on:
\begin{enumerate} \itemsep0em
\item aced this one.
\item total dispair, took years off my life.
\item I have a question: \textbf{why did you use $R$ (the gas constant), instead of $k$ (Boltzmann's constant) in Eq.~2 of solutions?}
\end{enumerate}

\noindent
Example of use of urls: \url{https://uwaterloo.ca}\\

\noindent
Examples of usage of the \verb$siunitx$ package: Planck's constant is $ \approx \SI{6.6e-34}{J \cdot s}$.  It's going to be a hot one today; we're expecting temperatures of $\SI{30}{\celsius}$.\\

\noindent
{\bf Some common latex errors:}\\

\noindent
If you need to use the symbols: \#, \%, or, \&, you must write them as: \verb$\%$, \verb$\%$, or \verb$\&$.  i.e., include a ``backslash'' \verb$\$ in front of the symbol.  This backslash is required because these characters have a special meaning in the ``language'' of latex.\\

\noindent
{\bf Some useful latex resources:}\\

\begin{enumerate}
\item
For figuring out the latex command for various symbols:
\url{http://detexify.kirelabs.org/classify.html}

\item
For converting images of equations to latex:
\url{https://youtu.be/j5iryTEJPsE}
\end{enumerate}

\noindent
{\bf Some common communication errors:}\\

\noindent
The single most important advice on technical writing that I have gotten is on usage of the word ``this''.  A nice example is given in Alley's {\em The craft of scientific writing, 4th ed. (Springer, 2018)}:
\begin{quotation}\noindent
No peaks occur in the olefinic region. Therefore, no significant concentration of olefinic hydrocarbons exists in fresh oil. This places an upper limit on the concentration of olefins --- no more than 0.01 percent.
\end{quotation}
The problem is: what does ``this'' refer to?  Quoting Alley: \textit{What does the chemist want the word ``this'' to refer to? To the last noun of the previous sentence: ``oil''? To the subject of the last sentence: ``concentration''? To the idea of the previous sentence: that no significant concentration of olefinic hydrocarbons exists? Actually, the word ``this'' in this example refers to none of these. The chemist intended the word ``this'' to refer to the lack of peaks in the olefinic region.}
Much improved is:
\begin{quotation}\noindent
The chromatogram has no peaks in the olefinic region. Therefore, no significant concentration of olefinic hydrocarbons exists in fresh oil. This chromatogram finding places an upper limit on the olefin concentration --- no more than 0.01 percent.
\end{quotation}
To summarize: always make it explicit what the word ``this'' refers to.\\

% DELETE UP TO THIS POINT

\end{document}
